Using reference models in variable selection \vspace{.1in}

### 2020-04-26 paper/ref_approach.tex
spell check

\subsection{Bodyfat example: Part 1}
\label{bodyfat-1}

@@

The target variable of interest is the amount of body fat, which is
obtained by a complex and expensive procedure consisting in immersing a 
person in a water tank and carrying out different measuraments and computations. 
Additionally, we have information about 13
variables which are anthropometric measurements (e.g., height, weight
and circumference of different body parts). The
variables are highly correlated which causes additional
challenge in the variable selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of body fat well while requiring the least amount of
measurements for a new person.

@@

The first two rows of Table \ref{tab:model_performances} show the
predictive performances, in terms of cross-validated root mean square
error (RMSE), of the full model and the selected models using projpred
or steplm.  There is no signfiant difference in predictive performance
of the selected models by different approaches even if there is
difference in the selected variables. This can be explained by high
correlation between the variables and different combinations can
provide similar predictive accuracy.

@@

Another main result of this paper is that the projective prediction
approach shows superior performance in minimal subset variable
selection compared to alternative methods whether or not these methods
make use of a reference model. That is, while the reference model is
certainly one important aspect the projective prediction approach, it
is not the only reason for its superior performance.  Rather, by
incoporating the full uncertainty of the posterior predictive
distribution into the variable selection procedure (instead of just
using point estimates) and using principled cross-validation method,
projective predictions combine several desirable variables into a
single procedure \citep{paper:projpred}.  In summary, we would
strongly recommend using projective predictions for minimal subset
 variable selection if possible and feasible. 
 However, if this is not an option in a given
situation, we would in any case recommend using a reference model on
top of the chosen variable selection method.

>>>>

\subsection{Body fat example: Part 1}
\label{bodyfat-1}

@@

The target variable of interest is the amount of body fat, which is
obtained by a complex and expensive procedure consisting in immersing a 
person in a water tank and carrying out different measurements and computations. 
Additionally, we have information about 13
variables which are anthropometric measurements (e.g., height, weight
and circumference of different body parts). The
variables are highly correlated which causes additional
challenge in the variable selection. In total, we have 251
observations. The goal is to find the model which is able to predict
the amount of body fat well while requiring the least amount of
measurements for a new person.

@@

The first two rows of Table \ref{tab:model_performances} show the
predictive performances, in terms of cross-validated root mean square
error (RMSE), of the full model and the selected models using projpred
or steplm.  There is no significant difference in predictive performance
of the selected models by different approaches even if there is
difference in the selected variables. This can be explained by high
correlation between the variables and different combinations can
provide similar predictive accuracy.

@@

Another main result of this paper is that the projective prediction
approach shows superior performance in minimal subset variable
selection compared to alternative methods whether or not these methods
make use of a reference model. That is, while the reference model is
certainly one important aspect the projective prediction approach, it
is not the only reason for its superior performance.  Rather, by
incorporating the full uncertainty of the posterior predictive
distribution into the variable selection procedure (instead of just
using point estimates) and using principled cross-validation method,
projective predictions combine several desirable variables into a
single procedure \citep{paper:projpred}.  In summary, we would
strongly recommend using projective predictions for minimal subset
 variable selection if possible and feasible. 
 However, if this is not an option in a given
situation, we would in any case recommend using a reference model on
top of the chosen variable selection method.
